Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
changing the rate, to 1/sampled lognormal variable. It is a longer tail for higher numbers

# range <- c(-0.9,5)
#create density plots
curve(dexp(x, m_1[5]), 
      #from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 1:4){
  curve(dexp(x, m_1[i]), 
        #from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}

>>>>

range <- c(-0.1,12)
#create density plots
curve(dexp(x, 1/m_1[1]), 
      from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 2:5){
  curve(dexp(x, 1/m_1[i]), 
        from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}
